Beliefs about the development of mental life

### 2021-08-02 supplement/supplement-main.Rmd
minor tweaks to text

---
title: "Beliefs about the development of mental life"
subtitle: "Supplemental Materials"
author: "[authors removed to preserve anonymity]"
date: "July 31, 2021"
output:
  # word_document:
  #   reference_docx: word-styles-ref.docx
   bookdown::pdf_document2:
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 3
bibliography: "references.bib"
# cls: "article.cls"
csl: nature.csl
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{float}
tables: yes
---

@@

In these Supplemental Materials, we provide extended information about the results presented in the main paper, present additional results, and provide an item-by-item comparison of the capacity items used here to items used in previous work on mind perception [@gray.etal2007, @weisman.etal2017a, @weisman.etal2017b, @malle2019].

@@

Study 1 also offered a first glimpse into US adults' perceptions of the development of mental life. Supplementary Figure \@ref(fig:figS03) provides a visualization of mean "scores" for each domain of mental life. To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensations_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabcapcomp)); for each participant, we then took the average of their responses to capacities in each domain at each target age. As we go on to confirm in Studies 2-3, this visualization suggests that participants perceived capacities for _bodily sensations_ to be substantial at birth and to develop relatively little over the first five years of life; in contrast, they perceived capacities for _negative affect_, _social connection_, and in particular _cognition and control_ to be much more limited at birth and to development dramatically over the first five years of life.

>>>>

---
title: "Beliefs about the development of mental life"
subtitle: "Supplemental Materials"
author: "[authors removed to preserve anonymity]"
date: "August 2, 2021"
output:
  # word_document:
  #   reference_docx: word-styles-ref.docx
   bookdown::pdf_document2:
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 3
bibliography: "references.bib"
# cls: "article.cls"
csl: nature.csl
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{float}
tables: yes
---

@@

In these Supplemental Materials, we provide extended information about the results presented in the main paper, present additional results, and provide an item-by-item comparison of the capacity items used here to items used in previous work on mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].

@@

Study 1 also offered a first glimpse into US adults' perceptions of the development of mental life. Supplementary Figure \@ref(fig:figS03) provides a visualization of mean "scores" for each domain of mental life. To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensations_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabs1efaparload)); for each participant, we then took the average of their responses to capacities in each domain at each target age. As we go on to confirm in Studies 2-3, this visualization suggests that participants perceived capacities for _bodily sensations_ to be substantial at birth and to develop relatively little over the first five years of life; in contrast, they perceived capacities for _negative affect_, _social connection_, and in particular _cognition and control_ to be much more limited at birth and to development dramatically over the first five years of life.
